\section{Learning Outcomes}
This internship provided invaluable lessons in both technical development and professional growth. The key takeaways include:

\begin{itemize}
    \item \textbf{Frontend Development with Next.js:} I honed my skills in building fast, responsive interfaces with Next.js. I learned how to organize components, implement dynamic features like chat, and optimize performance for better user experience.

    \item \textbf{Real-Time Communication with Socket.IO:} Building the chat feature using Socket.IO allowed me to understand how real-time data works. The instant messaging feature taught me the importance of real-time communication in web applications.

    \item \textbf{Leo Assistant Implementation:} Developing Leo, the smart assistant, gave me hands-on experience in building interactive workflows for users. I learned how to create guided conversations that lead to actionable outcomes, like project estimation and service booking, based on the user's input.

    \item \textbf{Team Collaboration:} Working closely with backend developers and other team members helped me improve my communication and collaboration skills. I learned to align my work with the backend team's efforts and solve integration issues efficiently.

    \item \textbf{Problem-Solving and Debugging:} Throughout the internship, I encountered various bugs and performance issues—whether related to slow pages, broken forms, or chat message delays. This experience strengthened my problem-solving skills and taught me how to approach challenges systematically.

    \item \textbf{User-Centered Design:} Enhancing the dashboards and user flows deepened my understanding of designing with the user in mind. This is particularly crucial for platforms like Maison Architecture, which cater to a specific audience (French clients and professionals). I realized how important it is to simplify complex processes and ensure accessibility.
\end{itemize}
