\section{Description of the Project(s) Involved During Internship}

The \textbf{Maison Architecture} project is an advanced platform designed to connect French clients with trusted architects and builders for their renovation and construction needs. The platform is organized into distinct sections to provide a tailored experience for each type of user:

\subsection{Customer Dashboard}
\begin{itemize}
    \item Clients can track their \textbf{orders and inquiries}, manage \textbf{billing information}, and use a variety of other essential features.
    \item \textbf{Hiring Partners:} Customers can search for and hire professionals by reviewing profiles, portfolios, and client feedback.
    \item \textbf{Messaging System:} A built-in messaging system allows seamless communication between customers and partners, ensuring clear and effective exchanges.
\end{itemize}

\subsection{Partner Dashboard}
\begin{itemize}
    \item \textbf{Profile and Portfolio Management:} Architects and builders can create detailed profiles and portfolios, showcasing their work, certifications, and services.
    \item \textbf{Document Submission \& Visibility Status:} Partners can submit necessary documents and track the visibility status of their profiles, ensuring they are visible to potential clients.
    \item \textbf{Project Bidding \& Customer Contact:} Partners can bid on posted projects, contact customers, and offer proposals to meet client needs.
\end{itemize}

\subsection{Admin Dashboard}
\begin{itemize}
    \item \textbf{Enterprise and Project Management:} Admin users have full control over managing the platform's \textbf{enterprises}, \textbf{project 360}, and \textbf{service offerings}.
    \item \textbf{Service Creation \& Blog Management:} Admins can create new services, post blog articles, and manage content.
    \item \textbf{Performance Tracking:} Admin users can track platform performance, monitor orders and inquiries, and oversee project metrics.
    \item \textbf{Partner Verification \& Messaging:} Admins have the ability to verify partner profiles and facilitate communication between customers and professionals.
\end{itemize}

\subsection{Maison Architecture Website}
\begin{itemize}
    \item The website hosts a large directory of \textbf{7,000+ enterprises} in the architecture and construction sector, offering clients a wide range of options.
    \item Users can apply for bookings, create orders, and explore various services such as \textbf{AI Assistant (Leo)}, \textbf{blog articles}, \textbf{professional portfolios}, and much more.
    \item \textbf{Leo Assistant}: An AI-powered assistant that guides clients through their project estimations, collects detailed information, generates cost estimates, and assists in making bookings once the requirements are clear. Leo ensures that all necessary data is gathered before proceeding with the project, creating a seamless experience for users.
    \item \textbf{Services and Expert Selection:} Clients can explore a broad list of services, read expert articles, and even select top-rated professionals for their projects.
    \item The website serves as an all-in-one hub for managing architectural services and projects, catering to both clients and professionals, making it easy to connect, plan, and execute renovation and construction projects.
\end{itemize}

The platform is designed to be user-friendly and efficient, helping clients and professionals manage their projects effectively while fostering a community of experts and service providers.