\section{Background Study}

\para{
The Maison Architecture project is rooted in modern web development technologies and service aggregation principles, specifically tailored to meet the demands of the architectural and construction sectors in France. This section explores the key theories, concepts, and terminologies that shape the foundation of the project.
}

\boldHeading{Web Development Technologies}
\para{
The platform's frontend is powered by Next.js, a React-based framework known for its support of server-side rendering and static site generation. These features enhance performance by reducing page load times and improving search engine optimization (SEO), making it ideal for a dynamic platform like Maison Architecture. Next.js enables real-time interactivity for users, particularly in features such as project listings and professional profiles \cite{vercel2023nextjs}.
}

\para{
On the backend, Nest.js—a progressive Node.js framework—ensures the platform is scalable, maintainable, and modular. It integrates seamlessly with GraphQL, which provides an efficient data-fetching solution. GraphQL allows users to query specific pieces of data, reducing unnecessary data transfer. This is particularly valuable for Maison Architecture, where different user roles, including clients, professionals, and admins, require access to tailored data.
}

\boldHeading{Service Aggregation Platforms}
\para{
Service aggregation platforms are intermediaries that connect service providers with clients via a centralized digital marketplace. These platforms facilitate discovery, communication, and transactions within specific industries. In the context of architecture and construction, examples such as Houzz and Thumbtack serve as inspiration. They help clients find qualified professionals for home renovations and new constructions. Maison Architecture emulates this model, providing a directory for French clients to explore vetted architects and builders, simplifying the process of hiring the right professional for their projects \cite{smith2020rise}.
}

\boldHeading{User Interface and Experience (UI/UX)}
\para{
The success of a platform like Maison Architecture heavily depends on its user interface and experience (UI/UX). For the platform to be successful, it must meet several key principles of design:
}

\begin{itemize}
    \item \textbf{Responsiveness:} The platform must be fully functional across various devices, ensuring it is accessible on desktop, tablet, and mobile devices.

    \item \textbf{Accessibility:} To ensure inclusivity, Maison Architecture adheres to accessibility standards such as WCAG (Web Content Accessibility Guidelines), ensuring that users of varying abilities can use the platform.

    \item \textbf{Clear Navigation:} Logical and easy-to-follow menus are vital for users to browse services, post projects, and track progress without confusion.

    \item \textbf{Feedback Mechanisms:} The platform should offer clear and timely feedback, such as confirmation messages after user actions, to maintain engagement and transparency.
\end{itemize}

\para{
These principles are essential in creating a user-friendly experience, particularly for users from both technical and non-technical backgrounds in the French architecture and construction market \cite{nielsen2018usability}.
}

