\section{Literature Review}

\para{
The literature review explores similar platforms, theories, and research findings relevant to Maison Architecture, providing insights into its potential impact as well as identifying challenges it may face. This section synthesizes academic studies, industry reports, and real-world examples to contextualize Maison Architecture within the broader digital transformation of the construction and architecture sectors.
}

\subsection{Similar Projects}
\para{
Several platforms offer comparable services to Maison Architecture, providing valuable lessons for its development.
}

\boldHeading{Architizer}
\para{
Architizer is a platform that connects architects with clients globally, allowing architects to showcase their portfolios and find new projects. Research by Johnson \cite{johnson2021impact} indicates that platforms like Architizer significantly increase architects' visibility by enabling clients to browse project galleries and read reviews from other users. This mirrors Maison Architecture’s goal of providing an easy-to-use platform for clients to discover professionals and gain inspiration from their work.
}

\boldHeading{Builder Trend}
\para{
Builder Trend is a project management tool that aids construction companies in improving communication and collaboration among stakeholders. Lee and Kim \cite{lee2022effect} found that tools like Builder Trend can greatly enhance project efficiency, reduce delays, and improve collaboration. Maison Architecture integrates similar real-time tracking and communication features to ensure smooth coordination among all parties involved in construction projects.
}

\boldHeading{Research on Service Aggregation}
\para{
A study by Patel \cite{patel2019economics} explores the economic benefits of online service platforms in the construction industry. These platforms foster competition and offer transparent pricing models that are particularly beneficial for clients seeking affordable architectural services in France.
}

\para{
Research by Chen and Liu \cite{chen2020role} emphasizes the importance of trust and reputation systems in online platforms. Their findings suggest that ratings, reviews, and user feedback are critical to user decision-making. Incorporating such systems in Maison Architecture will likely increase its credibility and attractiveness in a market where trust is a cornerstone of successful professional engagements.
}

\boldHeading{Digital Transformation in Construction}
\para{
The construction industry is undergoing a digital transformation, with platforms like Maison Architecture playing a key role in this evolution. McKinsey \cite{mckinsey2021digital} reports that digital tools can lead to significant improvements in productivity, quality, and sustainability within construction projects. However, challenges such as resistance to change, low digital literacy, and data security concerns remain prevalent \cite{wef2020shaping}.
}

\boldHeading{Synthesis and Implications}
\para{
This literature review demonstrates that Maison Architecture is part of a growing trend of digitalization in the architectural and construction sectors, particularly in France. By drawing insights from platforms like Architizer and Builder Trend and addressing the challenges identified in current research, Maison Architecture can enhance its effectiveness and appeal. Incorporating trust and reputation systems as suggested by Chen and Liu \cite{chen2020role} and focusing on productivity improvements \cite{mckinsey2021digital} will ensure that the platform meets its goal of providing seamless, efficient service for both clients and professionals.
}

\para{
Overall, this review lays a solid foundation for understanding the Maison Architecture project by integrating theoretical frameworks with practical insights—a crucial step in guiding its development and evaluation.
}
