\pagestyle{plain}
\chapter*{Acknowledgment}

\para{
I extend my sincere gratitude to all who contributed to the success of the \textit{\pgfkeysvalueof{/Project/title}} project. This achievement was made possible by the support and guidance of numerous individuals and institutions.
}

\para{
I express my deepest appreciation to my project supervisor, \textbf{\pgfkeysvalueof{/Project/letterOfApproval/approvers/supervisor/name}}, and Head of Department, \textbf{\pgfkeysvalueof{/Project/letterOfApproval/approvers/internalExaminer/name}}, for their invaluable expertise and insightful feedback, which were instrumental in shaping this project.
}

\para{
I also extend my sincere thanks to my mentor, \textbf{\pgfkeysvalueof{/Project/mentor/name}}, for their guidance and support throughout this internship. Their expertise and advice were invaluable in navigating the challenges encountered during this project.
}

\para{
I am grateful to the faculty and staff of \textbf{\pgfkeysvalueof{/Project/institute/college}}, affiliated with \textbf{\pgfkeysvalueof{/Project/institute/university}}, for fostering an environment of learning and innovation. Their dedication to academic excellence and commitment to providing the best educational resources have been integral to my journey.
}

\para{
My heartfelt thanks go to \textbf{Mr. Adish Kattel}, CEO of Hyteno, for providing the opportunity to work on this project and for his support throughout the internship. I also thank all my colleagues at Hyteno for their assistance and collaboration.
}

\para{
Finally, I acknowledge and appreciate everyone who contributed directly or indirectly to this project's success. Your collective support has been a driving force in this achievement.
}

\vfil
\begin{flushleft}
    With Gratitude\\
    \pgfkeysvalueof{/Project/authors/author1/name}\\
\end{flushleft}

\pagebreak
